Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-01-21 ms.tex
I added a tiny note about 2MASS 1821 MORIS reduction.
Made a table fit inside the page better and added an explanatory sentence to a figure caption.

\author{E. Schlawin\altaffilmark{1,2}, Adam J.\ Burgasser\altaffilmark{2,3}, J. Teske\altaffilmark{4}, J. Gizis\altaffilmark{5} \and T. Karalidi\altaffilmark{1}}

\altaffiltext{1}{Steward Observatory, Tucson AZ 85721 \email{eas342@email.arizona.edu}}
\altaffiltext{2}{Visiting Astronomer at the Infrared Telescope Facility, which is operated by the University of Hawaii under contract NNH14CK55B with the National Aeronautics and Space Administration}
\altaffiltext{3}{Center for Astrophysics and Space Science, University of California San Diego, La Jolla, CA 92093, USA}
\altaffiltext{4}{Carnegie DTM, 5241 Broad Branch Road, NV, Washington, DC 20015, USA}
\altaffiltext{5}{Department of Physics and Astronomy, University of Delaware, Newark, DE 19716, USA}

\begin{abstract}
Low-temperature L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres. The spectral character of these variations yield insight into the particle sizes and vertical structure of the clouds. Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility. By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth. We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.4\% per band) variability with no spectral dependence {\bf [THIS NEEDS TO BE CHECKED]}, while 2MASS~J1821+1414 varies by up to $\pm$2\% at 1~$\mu$m, the variability amplitude declining toward longer wavelengths.  {\bf [PHASE VARIATION]}. The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction of sub-micron dust particles, although this model becomes too strong at short wavelengths. An alternate model based on surface hot spots requires implausibly large temperature variations. The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.
\end{abstract}

@@

We identified potential targets for relative spectro-photometry by selecting among the $\approx$200 known L dwarfs\footnote{We identified these sources from DwarfArchives,  \url{http://dwarfarchives.org}. The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) visual binary companions at apparent separations of 5$\arcsec$--30$\arcsec$. We identified 30 potential targets, and prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.  Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).
2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C}) is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}. Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius R = 1~{\rjup}. There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}). 
2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G}. This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}, suggesting a near equator-on orientation.  \citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths. There are two suitably bright comparison stars within 20$\arcsec$ for relative calibration: 2MASS~J18212812+1414089 with $H$ = 12.6 at 7$\arcsec$ separation and 2MASS~J18212715+1413482 with $H$ = 12.0 at 29$\arcsec$ separation; we chose the latter for our monitoring observations.

\begin{deluxetable*}{llcccccccl}
\tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
\tablewidth{0pt}
\tablehead{
\colhead{Name} & 
\colhead{SpT} & 
\colhead{$d$} & 
\colhead{2MASS $H$} & 
\colhead{$J-K_s$} & 
\colhead{\teff} & 
\colhead{P$_{rot}$} &
\colhead{$v\sin{i}$} & 
\colhead{$i$\tablenotemark{a}} & 
\colhead{Refs} \\
 &  & \colhead{(pc)} & &  & \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($degree$)} \\
 }
\startdata
2MASS~J08354256$-$0819237 & L5 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
2MASS~J18212815+14140101 & L4.5pec & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1600$\pm$100 & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
\enddata
\tablenotetext{a}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.2$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s. A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.}
\tablenotetext{b}{Tentative period.}
\tablerefs{(1) \citet{2003AJ....126.2421C};
(2) \citet{2012ApJ...752...56F}; 
(3) \citet{2015ApJ...810..158F};
(4) \citet{2004MNRAS.354..378K};
(5) \citet{2010ApJ...723..684B};
(6) \citet{2008ApJ...686..528L}; 
(7) \citet{2016MNRAS.455..357S};
(8) \citet{2015ApJ...798...73G};
(9) \citet{2015ApJ...799..154M}
(10) \citet{2015ApJ...798L..13Y}; 
}
\end{deluxetable*}

\begin{figure*}
\centering
	\plottwo{image0835-0819.pdf}{image1821+1414.pdf}
	\label{fig:image1821}
	\caption{2MASS $JHK_s$ three-color images of the fields around our targets {\sha} (left) and {\shb} (right).  Each image is centered on the target, and span a 1$\arcmin\times\arcmin$ field of view oriented with North up and East the left. The comparison stars referred to in the text appear as blue sources in these images. }
	\label{fig:images}
	\vspace{0.1in}
\end{figure*}

To characterize the atmospheric regions probed by our observations, we computed the brightness temperature spectra of our sources using previously obtained IRFT/SpeX data \citep{2008ApJ...686..528L,2010ApJ...710.1142B}. The brightness temperature:
\begin{equation}
T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{I_{\lambda,surf}\lambda^5}\right)\right]^{-1}
\end{equation}
can be inferred from the surface flux density
\begin{equation}
I_{\lambda,surf} = {\pi}B_{\lambda} = I_{\lambda,obs}\left(\frac{d}{R}\right)^2 = I_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2
\end{equation}
where $I_{\lambda,obs}$ and $I_{\lambda,abs}$ are the observed and absolute flux densities, $d$ the source distance and $R$ the source radius.  For both sources, we first normalized the observed spectrum to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes \citep{2016MNRAS.455..357S,2016AJ....152...24W}, then adopted radii from the evolutionary models of \citet{2001RvMP...73..719B} assuming effective temperatures ({\teff}s) computed by \citet{2015ApJ...810..158F} based on bolometric luminosity measurements. Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\teff} and radius were propagated by Monte Carlo simulation.  \citet{2016ApJ...833...96L} have recently reported {\sha} to be both overluminous and exhibiting signatures of moderately low surface gravity; we therefore considered two cases for this source: an age of 200--500~Myr uniformly sampled, for which the evolutionary models predict radii of 0.115~R$_{\odot}$ to 0.101~R$_{\odot}$; and an equal-mass binary with the same age range ($I_{\lambda,int}$ = $\frac{1}{2}I_{\lambda,obs}$). For {\shb}, we assumed a uniform age range of 1--5~Gyr, for which the evolutionary models predict radii of 0.092~R$_{\odot}$ to 0.082~R$_{\odot}$.  Figure~\ref{fig:tbright} shows the resulting brightness temperature spectra and their uncertainties from these calculations.  The spectral peaks for {\shb} span 1950--2100~K, slightly warmer at short wavelengths. For {\sha}, the young single model predicts a peak brightness temperature that increases with wavelength, reaching 2450~K at $K$-band. Assuming this source is a binary brings the brightness temperature spectrum into qualitative (roughly flat) and quantitative (2100--2250~K) agreement with {\shb}. {\bf [I'M WORRIED I HAVE A FACTOR OF 2 ERROR HERE]}.

\begin{figure*}
\centering
	\plottwo{tbright0835.png}{tbright1821.png}
	\caption{Calculated brightness temperature of {\sha} (left) and {\shb} (right) as a function of wavelength. The faint lines represent individual calculations assuming a Monte Carlo realization of spectral flux, absolute magnitude, {\teff} and radius uncertainties; the dark lines represent the median of these realizations. For {\sha}, we calculate separately for young single (black) and binary (blue) models, the latter scaling the observed absolute fluxes by a factor of two. }
	\label{fig:tbright}
	\vspace{0.1in}
\end{figure*}

@@

We observed {\sha} and {\shb} for one night each with the IRTF/SpeX (Table \ref{tab:obsParam}).
{\sha} was observed for 4.65 hours, covering 1.5 rotation periods; {\shb} was observed for 7.47 hours, covering 1.8 rotation periods.
Following \citet{2014ApJ...783....5S}, we used SpeX in its prism-dispersed mode, obtaining 0.9--2.4~$\micron$ spectra in a single order at low dispersion. 
Both target and reference star were observed simultaneously by orienting the 3$\arcsec$$\times$60$\arcsec$ slit to align with the visual binary axis. This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes differental color refraction. The effective resolution of the spectral data, set by seeing and pointing errors, are $\lambda$/$\Delta\lambda$ $\approx$ 50. Integration times were 60~s and 45~s for {\sha} and {\shb}, respectively. The short-wavelength limit of our spectral coverage was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.
For {\sha} our MORIS exposures were 15~sec, which was sufficient for guiding but not precision photometry. For {\shb}, we were able to guide on sources in the SpeX imaging channel, so we increased the $i$-band exposures to 60~sec to obtain a simultaneous $i$-band light-curve.

@@

Wavelength calibrations were performed using observations of ThAr emission lamps with the 0$\farcs$3$\times$60$\arcsec$.
The images were rectified by shifting each row to match a center row in between the two sources.
This was achieved by cross correlating the reference row with all other detector rows (which have the same background spectrum) and fitting a smooth function over the sources as in \citealt{2016ApJ...826..156S}.
We also obtained calibration sequences of ThAr and flat-field incadescent lamps with the 3$\arcsec$$\times$60$\arcsec$ slit  before and after the brown dwarf time series.
% to measure pixel response and assess flexure in the instrument with telescope orientation.
For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response. 
To correct for instrument flexure, we also cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.
These shifts were used to apply a custom flat field for every image.

@@

{\bf [MORIS REDUCTION FOR 1821?]}

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
	\label{fig:specphot0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
	\label{fig:specphot1821}
	}
	\caption{Top Panels: Normalized median raw spectra of {\sha} (left) and {\shb} (right) in black, compared with the respective reference stars (blue) and background emission (red; mostly telluric OH emission and thermal background). These spectra have not been corrected for telluric absorption or instrumental spectral response. The reference stars have significantly bluer spectra than the brown dwarfs. Bottom Panels: Dynamic spectra of each brown dwarf system. [MORE DESCRIPTION]}
	\label{fig:specphot}
	\vspace{0.1in}
\end{figure*}

@@

Individual narrow-band light curves for extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}. The uncertainties in these curves are {\bf [WHAT? HOW DETERMINED?]}. Again, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m.  These variations are approximately sinusoidal, although we detect ``double-hump'' structures with slight downturns in flux at peak amplitudes around -3~hr and +1~hr. In the regions of strong telluric absorption, the variability pattern changes, with a U-shaped profile minimized at $-$1~hr. As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and ignore these regions in our subsequent analysis.
{\bf [WE SHOULD VERIFY THIS]}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
\caption{Sine fit amplitude versus wavelength excluding the wavelength regions contaminated by telluric absorption. with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m. Also shown in the figure is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage.}\label{fig:ampspec1821mie}
\end{centering}
\end{figure}

@@

The WFC3 amplitude spectrum is shown with the data in Figure \ref{fig:ampspec1821mie}.
There is a multiplicative offset between the IRTF and WFC3 spectrum because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
The WFC3 spectrum is not affected by the telluric absorption the way the SpeX data is.
\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and consistent with our Mie scattering fit.

>>>>

\author{E. Schlawin\altaffilmark{1,2}, Adam J.\ Burgasser\altaffilmark{2,3}, J. Gizis\altaffilmark{4}, T. Karalidi\altaffilmark{1}, \and J. Teske\altaffilmark{5}}

\altaffiltext{1}{Steward Observatory, Tucson AZ 85721 \email{eas342@email.arizona.edu}}
\altaffiltext{2}{Visiting Astronomer at the Infrared Telescope Facility, which is operated by the University of Hawaii under contract NNH14CK55B with the National Aeronautics and Space Administration}
\altaffiltext{3}{Center for Astrophysics and Space Science, University of California San Diego, La Jolla, CA 92093, USA}
\altaffiltext{4}{Department of Physics and Astronomy, University of Delaware, Newark, DE 19716, USA}
\altaffiltext{5}{Carnegie Observatories, 813 Santa Barbara Street, Pasadena, CA 91101, USA}

\begin{abstract}
Low-temperature L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres. The spectral character of these variations yield insight into the particle sizes and vertical structure of the clouds. Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility. By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth. We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.4\% per band) variability with no spectral dependence {\bf [THIS NEEDS TO BE CHECKED]}, while 2MASS~J1821+1414 varies by up to $\pm$2\% at 1~$\mu$m, with the variability amplitude declining toward longer wavelengths.  {\bf [PHASE VARIATION]}. The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction of sub-micron dust particles, although this model becomes too strong at short wavelengths. An alternate model based on surface hot spots requires implausibly large temperature variations. The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.
\end{abstract}

@@

We identified potential targets for relative spectro-photometry by selecting among the $\approx$200 known L dwarfs\footnote{We identified these sources from DwarfArchives,  \url{http://dwarfarchives.org}. The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) visual binary companions at apparent separations of 5$\arcsec$--30$\arcsec$. We identified 30 potential targets, and prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.  Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).

2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C} is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that shows signatures of low surface gravity \citep{2016ApJ...833...96L}. 
This source has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius R = 1~{\rjup}.
There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}). 
2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L}.
This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}, suggesting a near equator-on orientation.  \citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths.
There are two suitably bright comparison stars within 20$\arcsec$ for relative calibration: 2MASS~J18212812+1414089 with $H$ = 12.6 at 7$\arcsec$ separation and 2MASS~J18212715+1413482 with $H$ = 12.0 at 29$\arcsec$ separation; we chose the latter for our monitoring observations.

\begin{deluxetable*}{lllcccccccl}[t]
\tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
\tablewidth{0pt}
\tablehead{
 & \multicolumn{2}{c}{Spectral Type} \\
\colhead{Name} & 
\colhead{Opt} & 
\colhead{NIR} & 
\colhead{$d$} & 
\colhead{2MASS $H$} & 
\colhead{$J-K_s$} & 
\colhead{\teff} & 
\colhead{P$_{rot}$} &
\colhead{$v\sin{i}$} & 
\colhead{$i$\tablenotemark{a}} & 
\colhead{Refs} \\
 &  &  & \colhead{(pc)} & &  & \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($\degr$)} \\
 }
\startdata
\sha\ & L5 & L7 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
\shb\ & L4.5p & L5 & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1614$\pm$100\tablenotemark{c} & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
\enddata
\tablenotetext{a}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.2$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s. A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.}
\tablenotetext{b}{Tentative period.}
\tablenotetext{c}{Estimated from the \citet{2015ApJ...810..158F} {\teff}/spectral type relation.}
\tablerefs{(1) \citet{2003AJ....126.2421C};
(2) \citet{2012ApJ...752...56F}; 
(3) \citet{2015ApJ...810..158F};
(4) \citet{2004MNRAS.354..378K};
(5) \citet{2010ApJ...723..684B};
(6) \citet{2008ApJ...686..528L}; 
(7) \citet{2016MNRAS.455..357S};
(8) \citet{2015ApJ...798...73G};
(9) \citet{2015ApJ...799..154M}
(10) \citet{2015ApJ...798L..13Y}; 
}
\end{deluxetable*}

\begin{figure*}
\centering
	\plottwo{image0835-0819.pdf}{image1821+1414.pdf}
	\label{fig:image1821}
	\vspace{-.9in}
	\caption{2MASS $JHK_s$ three-color images of the fields around our targets {\sha} (left) and {\shb} (right).  Each image is centered on the target, and span a 1$\arcmin\times\arcmin$ field of view oriented with North up and East the left. The comparison stars referred to in the text appear as blue sources in these images. }
	\label{fig:images}
	\vspace{0.17in}
\end{figure*}

To characterize the atmospheric regions probed by our observations, we analyzed previously 
obtained IRTF/SpeX data for these sources \citep{2008ApJ...686..528L,2010ApJ...710.1142B}.
Direct comparison to spectral standards following the convention of \citet{2010ApJS..190..100K} indicate near-infrared
classifications of L7 for {\sha} and L5 for {\shb} (Figure~\ref{fig:tbright}). The former is considerably later than the L5 optical classification previously reported by \citet{2003AJ....126.2421C}. We confirm the intermediate low surface gravity classification (INT-G) reported by \citet{2016ApJ...833...96L} based on the indices of \citet{2013ApJ...772...79A} using an L7 classification. The discrepancy between the optical and near-infrared classifications of this source is likely related to surface gravity effects. {\shb}, on the other hand, is a good match to the L5 spectral standard and has a field dwarf gravity classification.

We computed brightness temperature spectra from these data as
\begin{equation}
T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{I_{\lambda,surf}\lambda^5}\right)\right]^{-1}
\end{equation}
where the surface flux density $I_{\lambda,surf}$ is computed as
\begin{equation}
I_{\lambda,surf} = {\pi}B_{\lambda} = I_{\lambda,obs}\left(\frac{d}{R}\right)^2 = I_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2
\end{equation}
$I_{\lambda,obs}$ and $I_{\lambda,abs}$ are the observed and absolute flux densities, $d$ the source distance and $R$ the source radius.  Both spectra were normalized to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes \citep{2016MNRAS.455..357S,2016AJ....152...24W}. We adopted radii from the evolutionary models of \citet{2003A&A...402..701B} assuming effective temperatures ({\teff}s) from \citet{2015ApJ...810..158F} based on these sources' bolometric luminosity measurements (Table~\ref{tab:bdProp}). Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\teff} and radius were propagated by Monte Carlo simulation.  For {\sha} we considered two cases: radii corresponding to an age of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}, for which the evolutionary models predict radii of 0.147~R$_{\odot}$ to 0.115~R$_{\odot}$; and an age range of 1--5~Gyr for which the evolutionary models predict radii of 0.092~R$_{\odot}$ to 0.084~R$_{\odot}$.
For {\shb}, we assumed a lower age limit of 200~Myr based on its FLD-G classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S} range of 1--5~Gyr; evolutionary models predict radii of 0.120~R$_{\odot}$ to 0.097~R$_{\odot}$ for these ages.

Figure~\ref{fig:tbright} shows the resulting brightness temperature spectra and their uncertainties from these calculations.  The spectral peaks for {\sha} are roughly constant at {\teff} = 1900$\pm$50~K in the field surface gravity case, and declines from 1700$\pm$20~K at the $J$-band peak to 1570$\pm$60~K at the $K$-band peak in the low surface gravity case. Spectra models (e.g., \citealt{2012RSPTA.370.2765A}) predict brightness temperatures closer to the effective temperature at the $JHK$ flux peaks, so these data suggest {\sha} has an intermediate age/radius compared the assumptions made here. For {\shb}, 
brightness temperatures range from 1880$\pm$30~K at the $J$-band peak to 1700$\pm$40~K at the $K$-band peak. These values are notably warmer than the {\teff} = 1614$\pm$100~K estimated from \citet{2015ApJ...810..158F} {\teff}/spectral type relation, but relatively consistent this source's earlier spectral type as compared to {\sha}. We conjecture that the Filippazzo et al.\ relation underestimates the {\teff} of this source due to its unusually dusty spectral energy distribution.

\begin{figure*}
\centering
	\plottwo{classify0835.pdf}{classify1821.pdf}
	\plottwo{tbright0835.pdf}{tbright1821.pdf}
	\caption{(Top) SpeX prism spectra (in black) of {\sha} (left; \citealt{2010ApJ...710.1142B}) and {\shb} (right; \citealt{2008ApJ...686..528L}) scaled to absolute flux densities, compared to their closest-match L dwarf spectral standards as defined in \citet[in red]{2010ApJS..190..100K}: the L7 2MASSI~J01033203+1935361 (data from \citealt{2014ApJ...794..143B}) and the L5 SDSS~J083506.16+195304.4 (data from \citealt{2006AJ....131.2722C}), respectively.  (Bottom) Calculated brightness temperature spectra of {\sha} (left) and {\shb} (right). The faint lines represent individual calculations assuming a Monte Carlo realization of spectral flux, absolute magnitude, {\teff} and radius uncertainties; the dark lines represent the median of these realizations. For {\sha}, we calculate separate brightness temperatures assuming radii consistent with a low surface gravity (50--200 Myr; blue) and field surface gravity (1--5~Gyr; black). }
	\label{fig:tbright}
	\vspace{0.1in}
\end{figure*}

@@

We observed {\sha} and {\shb} for one night each with the IRTF/SpeX (Table \ref{tab:obsParam}).
{\sha} was observed for 4.65 hours, covering 1.5 rotation periods; {\shb} was observed for 7.47 hours, covering 1.8 rotation periods.
Following \citet{2014ApJ...783....5S}, we used SpeX in its prism-dispersed mode, obtaining 0.9--2.4~$\micron$ spectra in a single order at low dispersion. 
Both target and reference star were observed simultaneously by orienting the 3$\arcsec$$\times$60$\arcsec$ slit to align with the visual binary axis. This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes differental color refraction. The effective resolution of the spectral data, set by seeing and pointing errors, are $\lambda$/$\Delta\lambda$ $\approx$ 50. Integration times were 60~s and 45~s for {\sha} and {\shb}, respectively. The short-wavelength limit of our spectral coverage was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.

%For {\sha} our MORIS exposures were 15~sec, which was sufficient for guiding but not precision photometry. For {\shb}, we were able to guide on sources in the SpeX imaging channel, so we increased the $i$-band exposures to 60~sec to obtain a simultaneous $i$-band light-curve.

@@

Wavelength calibrations were performed using observations of ThAr emission lamps with the 0$\farcs$3$\times$60$\arcsec$.

The images were rectified by shifting each row to match a center row in between the two sources.
This was achieved by cross correlating the reference row with all other detector rows (which have the same background spectrum) and fitting a smooth function over the sources as in \citealt{2016ApJ...826..156S}.
We also obtained calibration sequences of ThAr and flat-field incadescent lamps with the 3$\arcsec$$\times$60$\arcsec$ slit  before and after the brown dwarf time series.
% to measure pixel response and assess flexure in the instrument with telescope orientation.
For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response. 
To correct for instrument flexure, we also cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.
These shifts were used to apply a custom flat field for every image.

@@

For MORIS reduction, we used the raw files and performed aperture photometry with the IDL \texttt{aper} procedure using an aperture size of 6 pixels and a sky annulus of 8-11 pixels.
{\bf [MORIS REDUCTION FOR 1821?]}

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
	\label{fig:specphot0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
	\label{fig:specphot1821}
	}
	\caption{Top Panels: Normalized median raw spectra of {\sha} (left) and {\shb} (right) in black, compared with the respective reference stars (blue) and background emission (red; mostly telluric OH emission and thermal background). These spectra have not been corrected for telluric absorption or instrumental spectral response. The reference stars have significantly bluer spectra than the brown dwarfs. Bottom Panels: Dynamic spectra of each brown dwarf system. The dynamic spectrum for \sha\ shows no significant variability whereas there is a periodic modulation for \shb\ that decrease toward longer wavelengths. [MORE DESCRIPTION -- How should the reader interpret these dynamic spectra?]}
	\label{fig:specphot}
	\vspace{0.1in}
\end{figure*}

@@

Individual narrow-band light curves for extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}.
The uncertainties in these curves are 0.2\% in high throughput regions of the spectrum and 0.6\% per exposure.
The lower values are areas of high throughput and flux whereas the low values are near telluric absorption features or the edges of the spectrum.
We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period of the brown dwarfs and compare it to the expected photon + read noise.
In these wavelength bins, the standard deviations of the points is about 2$\times$ the expected read noise and photon noise.
We attribute this to correlated errors between wavelengths. {\bf [WHAT? HOW DETERMINED?]}

As seen in Figure~\ref{fig:tserPfold}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m.  These variations are approximately sinusoidal, although we detect ``double-hump'' structures with slight downturns in flux at peak amplitudes around -3~hr and +1~hr. In the regions of strong telluric absorption, the variability pattern changes, with a U-shaped profile minimized at $-$1~hr. As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and ignore these regions in our subsequent analysis.
{\bf [WE SHOULD VERIFY THIS]}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
\caption{Sine fit amplitude versus wavelength excluding the wavelength regions contaminated by telluric absorption. [SOMETHING HERE? like, The data are fit] with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m. Also shown in the figure is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage.}\label{fig:ampspec1821mie}
\end{centering}
\end{figure}

@@

The WFC3 amplitude spectrum is shown with the data in Figure \ref{fig:ampspec1821mie}.
There is a multiplicative offset between the IRTF and WFC3 spectrum because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
The WFC3 spectrum is not affected by the telluric absorption, unlike the SpeX data.
\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our Mie scattering fit.
